\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates

### 2022-06-07 analysis/paper/bhatnagar-turgeon-islam-hanley-saarela.Rmd
add paragraph on parsimonious model

>>>>

A more parsimonious model based on these results could be constructed as follows:

$$ \log \lambda\left(t \mid \mathbf{Z}\right) = \begin{cases} \alpha, &\quad t < t_0\\
\alpha + \beta Z(t - t_0), &\quad t \geq t_0\end{cases},$$
where $t_0 \approx 7$ years. This model corresponds to a hazard ratio that is constant and equal to 1 until $t = t_0$, after which it decreases exponentially. If we fix the value $t_0$, we can easily implement this model using our package; for example:

```{r, echo = TRUE, eval = FALSE}
fitSmoothHazard(DeadOfPrCa ~ as.integer(Follow.Up.Time >= t0) :
                    I(Follow.Up.Time - t0) : ScrArm,
                data = ERSPC)
```

\noindent Here, we use the binary variable `as.integer(Follow.Up.Time >= t0)` in order to write the two cases of our formula above in a more compact way. We also use the function `I()`, which allows us to specify new variables within the formula using normal `R` code. This is required, as otherwise the symbol `-` would be interpreted as a formula operator. Finally, we use the operator `:` instead of `*` in order to only include the interaction term, not the main effects.

Alternatively, the breakpoint $t_0$ could also be estimated by combining case-base sampling with segmented regression. However, this extension is beyond the current scope of `casebase`.

### 2022-06-07 analysis/paper/bhatnagar-turgeon-islam-hanley-saarela.tex
add paragraph on parsimonious model

>>>>

A more parsimonious model based on these results could be constructed as
follows:

\[ \log \lambda\left(t \mid \mathbf{Z}\right) = \begin{cases} \alpha, &\quad t < t_0\\
\alpha + \beta Z(t - t_0), &\quad t \geq t_0\end{cases},\] where
\(t_0 \approx 7\) years. This model corresponds to a hazard ratio that
is constant and equal to 1 until \(t = t_0\), after which it decreases
exponentially. If we fix the value \(t_0\), we can easily implement this
model using our package; for example:

\begin{Schunk}
\begin{Sinput}
fitSmoothHazard(DeadOfPrCa ~ as.integer(Follow.Up.Time >= t0) :
                    I(Follow.Up.Time - t0) : ScrArm,
                data = ERSPC)
\end{Sinput}
\end{Schunk}

\noindent Here, we use the binary variable
\texttt{as.integer(Follow.Up.Time\ \textgreater{}=\ t0)} in order to
write the two cases of our formula above in a more compact way. We also
use the function \texttt{I()}, which allows us to specify new variables
within the formula using normal \texttt{R} code. This is required, as
otherwise the symbol \texttt{-} would be interpreted as a formula
operator. Finally, we use the operator \texttt{:} instead of \texttt{*}
in order to only include the interaction term, not the main effects.

Alternatively, the breakpoint \(t_0\) could also be estimated by
combining case-base sampling with segmented regression. However, this
extension is beyond the current scope of \texttt{casebase}.
